Analysis on Trend of Death of Shelter Residence in Toronto 

### 2024-09-25 paper/paper.qmd
formatting add llm usage

\newpage
\appendix
# Appendix {#sec-appendix}
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Get first 10 lines in the data set as a sample
example_table <- shelter_death_data %>%
  slice(1:10)

@@

# References

>>>>

\newpage
\appendix

# Appendix {#sec-appendix}
Table 1 shows the a sample how data is like in the original dataset from @toronto_shelter_deaths provided by @opendatatoronto. It is the first 5 lines in the dataset.

Table 2 shows the summary of our dataset. It contains the total decedents number, monthly average deaths, minimum, maximum and median of the each year. It also provide the ratio of different gender in the shelter decedents each year.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Get first 20 lines in the data set as a sample
example_table <- shelter_death_data %>%
  slice(1:5)

@@

\newpage
# References
